Msc Thesis Figures

### 2020-08-20 docs/msc_thesis_figures.Rmd
finish splitting

# Final extracted datasets
df_final <- read_csv("../outputs/final/final_df_current_density.csv") %>%
  mutate(timestep = (timestep*10)+1990, source = "model", zone = as.factor(zone))
df_final_origin <- read_csv("../outputs/final/final_df_origin_current_density.csv") %>%
  mutate(timestep = timestep*10+1990, source = "model")

>>>>

# Final extracted datasets
df_final <- read_csv("../outputs/final/final_df_current_density_part1.csv") %>%
  bind_rows(read_csv("../outputs/final/final_df_current_density_part2.csv")) %>% 
  mutate(timestep = (timestep*10)+1990, source = "model", zone = as.factor(zone))
df_final_origin <- read_csv("../outputs/final/final_df_origin_current_density.csv") %>%
  mutate(timestep = timestep*10+1990, source = "model")
